\LARGE \bf Enhancing Security in Multi-Robot Systems through Co-Observation Planning on Unsecured Trajectories

### 2023-08-02 paper.tex
update from tron

\title{\LARGE \bf
 %Distributed Task Assignment for Cyber-Physical Security in Multi-Agent Systems
 Multi-agent cross-trajectory planning using graph theory}
 %with Applications to Cyber-Physical Security}
% with Applications to Introspection Monitoring}
\author{Ziqi Yang and Roberto Tron\thanks{This project is supported by the National Science Foundation grant "CPS: Medium: Collaborative Research: Multiagent Physical Cognition and Control Synthesis Against Cyber Attacks" (Award number 1932162).}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
This paper addresses the critical issue of security in multi-robot systems (MRS) when facing threats from adversaries attempting to compromise the robots' control. Such compromises could lead to unauthorized access to forbidden areas, potentially causing harm or disrupting the mission. To tackle this problem, we propose a novel multi-robot planning algorithm that leverages mutual observations between robots as an additional security measure. Our approach guarantees that even in the face of adversarial movement by attackers, compromised robots cannot reach forbidden regions without missing scheduled co-observations. We achieve this by introducing \emph{reachability} constraints into the previously developed continuous trajectory planning algorithm. These constraints ensure an empty intersection between the sets of locations that the agents could potentially reach and the forbidden regions. Furthermore, to enhance system resilience, we introduce the concept of \emph{sub-teams}, where multiple robots form cohesive units along each route, replacing individual robot assignments. This redundancy enables robots to deviate from their assigned sub-teams and join others to perform cross-trajectory co-observations, thereby securing multiple trajectories simultaneously. To efficiently plan cross-trajectory co-observations that maintain security against plan-deviation attacks, we formulate the multi-flow problem on unsecured MRS trajectories. We demonstrate the effectiveness and robustness of our proposed algorithm, which significantly strengthens the security of multi-robot systems in the face of adversarial threats.
\end{abstract}

>>>>

\title{\LARGE \bf

Enhancing Security in Multi-Robot Systems through Co-Observation Planning on Unsecured Trajectories}

\author{Ziqi Yang and Roberto Tron\thanks{This project is supported by the National Science Foundation grant "CPS: Medium: Collaborative Research: Multiagent Physical Cognition and Control Synthesis Against Cyber Attacks" (Award number 1932162).}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
This paper addresses the critical issue of security in multi-robot systems (MRS) when facing threats from adversaries attempting to compromise the robots' control. Such compromises could lead to unauthorized access to forbidden areas, potentially causing harm or disrupting the mission. To tackle this problem, we propose a novel multi-robot planning algorithm that leverages mutual observations between robots as an additional security measure. Our approach guarantees that even in the face of adversarial movement by attackers, compromised robots cannot reach forbidden regions without missing scheduled co-observations. 
We achieve this by introducing \emph{reachability} constraints into continuous trajectory planning algorithm. These constraints ensure an empty intersection between the sets of locations that the agents could potentially reach and the forbidden regions. 
\rtron{The reachability constraint is implemented with ellipsoidal over-approximation; this allows to quickly check intersection and compute gradients.}
Furthermore, to enhance system resilience and feasibility of the planning problem, we introduce the concept of \emph{sub-teams}, where multiple robots form cohesive units along each route, replacing individual robot assignments. This redundancy enables robots to deviate from their assigned sub-teams and join others to perform cross-trajectory co-observations, thereby securing multiple trajectories simultaneously. To efficiently plan cross-trajectory co-observations that maintain security against plan-deviation attacks, we formulate the multi-flow problem on unsecured MRS trajectories. 
\rtron{This second part fixes the feasiblity problems of the first one, and uses the same reacheability constraints to build inter-team trajectories.}
We demonstrate the effectiveness and robustness of our proposed algorithm, which significantly strengthens the security of multi-robot systems in the face of adversarial threats.
\end{abstract}
